Think deep for reef resilience

### 2025-07-10 paper/paper_draft.qmd
Improve grouped timeseries plotting and increase sizes/dpi
Also move model info to supplementary

CoralBlox is a coral population growth and mortality model that simulates groups of corals growing in diameter and competing for limited space over time [@ribeirodealmeida2024]. This model incorporates linear extension (growth) and background mortality rates that are dependent on the size and functional group of a coral colony. Environmental disturbances and reproduction are not directly considered within CoralBlox. Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform [@iwanaga2023]. Within ADRIA, we incorporate coral life history and environmental events in the following order: coral colony growth; coral reproduction; larval connectivity and settlement; and coral bleaching due to heat stress. As ADRIA and CoralBlox are coupled together to represent the system, we refer to both as ADRIA-CoralBlox.

@@

## Model parameterisation

>>>>

CoralBlox is a coral population growth and mortality model that simulates groups of corals growing in diameter and competing for limited space over time [@ribeirodealmeida2024]. Details on how coral demographic processes are implemented in ADRIA - CoralBlox can be found in the supplementary material [**link ADRIA - CoralBlox**].

@@

## ADRIA - CoralBlox
CoralBlox model incorporates linear extension (growth) and background mortality rates that are dependent on the size and functional group of a coral colony. Environmental disturbances and reproduction are not directly considered within CoralBlox. Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform [@iwanaga2023]. Within ADRIA, we incorporate coral life history and environmental events in the following order: coral colony growth; coral reproduction; larval connectivity and settlement; and coral bleaching due to heat stress. As ADRIA and CoralBlox are coupled together to represent the system, we refer to both as ADRIA-CoralBlox.

### Model parameterisation
